SI

### 2021-02-03 ms/manuscript.Rmd
Update MS

# Intergenerational Niche Differentiation in Filmy Ferns (Hymenophyllaceae)

@@

Despite this considerable interest in filmy fern ecophysiology, with the sole exception of @Johnson2000, no studies have compared physiology between gametophyte and sporophyte phases, and we are aware of none that have done so across multiple species.
Furthermore, to our knowledge, no physiological studies of filmy ferns have accounted for their phylogenetic relationships, and we lack an understanding of how physiological strategies have evolved in this clade.
In addition to DT, photosynthetic optima (adaptation to different light levels) are likely to be important in determining the niches of life stages and species of filmy ferns [@Proctor2003; @Parra2015; @Flores-Bavestrello2016].
Terrestrial and epiphytic species experience different levels of photosynthetic radiation and desiccation, and light intensity varies with height along the host plant in epiphytes [@Benzing1990; @WatkinsJr.2009].
In a recent study (Testo et al., unpublished), the combined effect of desiccation and light stress was found to have a greater impact on filmy fern physiological performance than either of these stressors alone, suggesting the need to integrate studies of DT with photosynthesis to gain a full picture of physiological adaptation in filmy ferns.
Here, we leverage a recently developed DNA barcoding system [@Nitta2017] to test several hypotheses related to DT and photosynthesis in a comparative phylogenetic framework including both filmy fern sporophytes and gametophytes: 
1.) Epiphytic filmy ferns have higher DT and photosynthetic optima than terrestrial species.
2.) Degree of DT is correlated with environmental water availability.
3.) Gametophytes with wider ranges have higher DT than those with with narrower ranges.

@@

@@

Results of the tests for phylogenetic signal (Blomberg's *K* and Pagel's λ*)* were similar for sporophytes and gametophytes, revealing significant phylogenetic signal for DT (gametophytes *K* and λ both near 1, *P \<*0.05; sporophytes *K* = `r sporo_recover_k`, *P* = `r sporo_recover_k_pval` and λ = `r sporo_recover_lambda`, *P* = `r sporo_recover_lambda_pval`), but no signal for PPFD~95%~ or ETR~max~ (`r table("physig")`).

@@

Relative humidity in the growth chambers was high when samples were first inserted, then gradually decreased to the target value maintained by each drying salt (\figs `r s_figure_num("chamber-s")`, `r s_figure_num("chamber-g")`).
Brief fluctuations to higher humidities were observed when chambers were opened to insert or remove samples (`r s_figure("chamber-s")`).

The GLMM including the effect of generation only was selected as the best-fitting model for DT (`r table("glmm")`). 
Sporophytes had `r sporo_dt_effect_mean` greater DT (95% CI `r sporo_dt_effect_lower` to `r sporo_dt_effect_upper`) relative to gametophytes (`r table("glmm-pars")`).

@@

We found a wide variation of DT in filmy fern sporophytes on Moorea, from no tolerance in terrestrial species to tolerance of water potentials well below -200 MPa in some epiphytes.
Levels of similarly extreme DT have also been reported in other species of *Hymenophyllum* [@Proctor2003; @Proctor2012] and a general correlation of habitat with DT in filmy ferns has been previously established [@Shreve1911; @Proctor2003; @Proctor2012; @Parra2009; @Saldana2013], but no other studies to our knowledge have documented a similar range of DT values in filmy ferns from a single site.
One may wonder then, what is the adaptive significance of being able to withstand drying at -200 MPa vs. -100 MPa when the ambient water potential is typically > -5 MPa and only rarely, if ever, drops below -50 MPa.
The recent finding of a constitutive mechanism for DT in filmy ferns [@GarcesCea2014] supports the need for a relatively wide "safety margin," and similar (or even more extreme) levels of constitutive DT are well known in bryophytes [@Oliver1993].
The conservative behavior of fern stomata, which lack a response to the plant stress hormone ABA, is well documented [@Brodribb2011; @Mcadam2012; @Mcadam2013].
It is possible that filmy ferns also behave conservatively with respect to water-stress.
We suggest that the variation in DT observed here is relevant because it is correlated with habitat, and likely reflects overall physiological tolerance, not just artificial extremes.
For example, sporophytes of some high elevation epiphytes that we surveyed (*C. minutum* var. 2, *H. digitatum*, *H. multifidum*, *H. polyanthos*) seem to be able to better withstand intense vs. moderate desiccation, with higher recovery values at -282 and -86 MPa vs. -38 MPa when dry for 15 d.
This may be an adaptation to cloud forest conditions; although cloud forests are frequently moist due to constant fog, dry periods are intense during the times when there is no cloud cover.
The complete lack of DT in terrestrial species is not surprising, considering they have much more direct access to water than epiphytes and therefore substantially less selective pressure to maintain DT.
Since controls kept at 100% RH maintained F~v~/F~m~ values near pre-treatment levels in all sporophytes (Appendix S3), it is unlikely that the lack of tolerance seen in terrestrial species is due solely to removal from the soil.
Comparison of DT with the minimum water potential envelope of each species (`r figure("corr")`) indicates that sporophytes of non-tolerant terrestrial and saxicolous species may not be able to occur in habitats with minimum water potential exceeding \circa{ }-7 MPa.
In contrast, habitats with minimum water potential below -7 MPa are nearly all epiphytic, and the filmy fern sporophytes occurring there are all capable of DT.

@@

Contrary to our hypotheses, gametophytes of filmy ferns are in general not more tolerant of the abiotic environment (light levels and water potential) than sporophytes.
This differs from other fern groups with desiccation tolerant gametophytes but desiccation sensitive sporophytes [@WatkinsJr.2007c].
In the filmy ferns we studied, DT levels of both sporophytes and gametophytes largely reflected habitat; in general, epiphytic species tended to have higher DT than terrestrial or saxicolous species, regardless of life stage.
Interestingly, this echoes much earlier field observations (not experimental data) by @Holloway1930 on filmy fern gametophytes in New Zealand: he reported apparent DT in gametophytes of *Hymenophyllum rarum* R. Br. and *H. villosum* Colenso, both high elevation epiphytes with desiccation tolerant sporophytes, and lack of DT in terrestrial filamentous gametophytes of *Polyphlebium colensoi* (Hook.) Ebihara & K. Iwats., *Abrodictyum strictum* (Menzies ex Hook. & Grev.) Ebihara & K. Iwats., and *A. elongatum* (A. Cunn.) Ebihara & K. Iwats. occupying moist, protected sites on the forest floor.
@WatkinsJr.2007c also found that DT of fern gametophytes tended to match habitat, with terrestrial species having lower DT than epiphytes.
However, we found that within high elevation epiphytes, gametophytes had lower DT than sporophytes, and only one species (saxicolous *P. endlicherianum*) with gametophytes that had significantly greater DT than sporophytes (`r figure("compare")`).
At high elevation sites (\ie, cloud forest), epiphytic ferns often occur in a dense matrix of bryophytes (Fig. 1B).
It is possible that this bryophyte cover helps to retain moisture during brief periods of drought and thus protect the epiphytic fern gametophytes that grow amongst them.
More detailed studies of the high elevation epiphytic environment and interactions between co-occurring gametophytes of ferns and bryophytes are needed to test this hypothesis.

Although we predicted that species with gametophytes that occur beyond the range of their sporophytes would have higher DT and be adapted for higher light levels, this was not the case.
This is perhaps best illustrated by *C. apiifolia* (`r figure("habit")`d, e, h).
Sporophytes of this species are usually restricted to moist cloud forest sites from \circa{ }600 m to 1200 m, but we observed gametophytes over a much wider range, down to 200 m.
A similar distribution pattern has been reported in congeneric *Callistopteris baldwinii* (D. C. Eaton) Copel.
from Hawaii [@Dassler1997].
Since gametophytes of *C. apiifolia* are common on Moorea and have a unique morphology [@Nitta2017], we were able to collect enough material of this species for additional tests of DT at higher humidity levels (48 h at 75% and 100% RH; results not shown).
However, it still failed to recover from even these gentle treatments.
This suggests that the widespread gametophytes of *C. apiifolia* do not rely on DT to attain their distribution, but instead must do so via some other mechanism.
Although we measured terrestrial microhabitats by positioning sensors a few cm above the ground, these sensors are still outside of the boundary layer.
It is likely that the gametophytes of *C. apiifolia* do not actually experience the conditions measured with our 'terrestrial' dataloggers, but instead grow within a much more consistently moist boundary layer.
Gametophytes of *C. apiifolia* produce gemmae (`r figure("habit")`e, h), and often form dense clonal mats.
In the case that their microhabitats do become too dry, they may suffer loss at the edge of the population, then recover by clonal growth [@Farrar2008].
Furthermore, the complex surface of clonal mats has been shown to increase the boundary layer and decrease evaporation rates in mosses [@Rice2001], and may function similarly in *C. apiifolia*.
Other filmy fern species also produce gemmae, but they are much more frequent in *C. apiifolia*, and the large size of the clonal mats formed by *C. apiifolia* indicate that it may have a high growth rate (J. Nitta, pers. obs.).
It is possible that there is a tradeoff between growth rate and DT, such that species capable of rapid asexual growth like *C. apiifolia* are unable to tolerate desiccation, but slower growing epiphytes such as *Hymenophyllum* spp.
can better tolerate it [@Oliver2000].
Growth rates of tolerant and non-tolerant gametophytes including quantification of gemmae production should be investigated in these species to test this hypothesis.

@@

Unlike DT, photosynthetic parameters did not vary significantly between species from different habitats.
Rather, we observed a clear intergenerational difference, with gametophytes consistently adapted for lower light levels than sporophytes (`r figure("combined")`, `r table("glmm")`).
In the only other study to our knowledge that compared photosynthetic rates between gametophytes and sporophytes of a filmy fern, @Johnson2000 also found that gametophytes of *V. speciosa* reached maximum ETR at lower levels than sporophytes: in gametophytes of this species, photosynthesis became saturated at a PPFD of 4--5 µmol·m^-2^·s^-1^ in the field or 30--50 µmol·m^-2^·s^-1^ in the lab vs. 30--50 µmol·m^-2^ ·s^-1^ for sporophytes (lab measurement only).
Although we found similar differences in direction between gametophytes and sporophytes, the measurements of @Johnson2000 are considerably lower than what we observed in the field for both Moorean filmy fern gametophytes (PPFD~95%~ \circa{ }40--60 µmol·m^-2^·s^-1^) and sporophytes (PPFD~95%~ \circa{ }130--160 µmol·m^-2^·s^-1^).
This makes sense in light of the fact that *V. speciosa* is an extremely deep-shade plant, with gametophytes occupying protected rock crevices that receive less than 1 µmol·m^-2^·s^-1^ PPFD for most of the day [@Johnson2000]; many of the gametophytes sampled in our study occur in more exposed conditions.
It is surprising, however, that we did not observe any differences between species in different habitats, given that light levels should vary between tree trunks and the forest floor, at least on a \circa{ }1 m scale.
It is possible that the actual light levels experienced by gametophytes growing in these habitats may not vary significantly if they occupy protected microsites such as bryophyte mats or crevices in rock or bark.

>>>>

# Intergenerational niche differentiation in filmy ferns (Hymenophyllaceae)

@@

Despite this considerable interest in filmy fern ecophysiology, with the sole exception of @Johnson2000, no studies have compared physiology between gametophyte and sporophyte phases, and we are aware of none that have done so across multiple species.
Furthermore, to our knowledge, no physiological studies of filmy ferns have accounted for their phylogenetic relationships, and we lack an understanding of how physiological strategies have evolved in this clade.
In addition to DT, photosynthetic optima (adaptation to different light levels) are likely to be important in determining the niches of life stages and species of filmy ferns [@Proctor2003; @Parra2015; @Flores-Bavestrello2016].
Terrestrial and epiphytic species experience different levels of photosynthetic radiation and desiccation, and light intensity varies with height along the host plant in epiphytes [@Benzing1990; @WatkinsJr.2009].
In a recent study (Testo et al., unpublished), the combined effect of desiccation and light stress was found to have a greater impact on filmy fern physiological performance than either of these stressors alone, suggesting the need to integrate studies of DT with photosynthesis to gain a full picture of physiological adaptation in filmy ferns.
Here, we leverage a recently developed DNA barcoding system [@Nitta2017] to test several hypotheses related to DT and photosynthesis in a comparative phylogenetic framework including both filmy fern sporophytes and gametophytes: 
1.) Light responses and DT differ between species with different growth habits.
2.) Light responses and DT differ between sporophytes and gametophytes.
3.) DT increases with decreasing environmental water availability.
4.) Gametophytes with wider ranges have higher DT than those with with narrower ranges.

@@

gameto_recover_k <- phylosig %>% filter(generation == "gametophyte", trait == "recovery_mean") %>% pull(kval) %>% round_t(2)
gameto_recover_k_pval <- phylosig %>% filter(generation == "gametophyte", trait == "recovery_mean") %>% pull(k_pval) %>% round_t(3)
gameto_recover_lambda <- phylosig %>% filter(generation == "gametophyte", trait == "recovery_mean") %>% pull(lambda) %>% round_t(2)
gameto_recover_lambda_pval <- phylosig %>% filter(generation == "gametophyte", trait == "recovery_mean") %>% pull(lambda_pval) %>% round_t(3)

@@

Results of the tests for phylogenetic signal (Blomberg's *K* and Pagel's λ*)* were similar for sporophytes and gametophytes, revealing significant phylogenetic signal for DT (gametophytes *K* = `r gameto_recover_k`, *P* = `r gameto_recover_k_pval` and λ = `r gameto_recover_lambda`, *P* = `r gameto_recover_lambda_pval`; sporophytes *K* = `r sporo_recover_k`, *P* = `r sporo_recover_k_pval` and λ = `r sporo_recover_lambda`, *P* = `r sporo_recover_lambda_pval`), but no significant signal for PPFD~95%~ or ETR~max~ (`r table("physig")`).

@@

Relative humidity in the growth chambers was high when samples were first inserted, then gradually decreased to the target value maintained by each drying salt (\figs{ }`r s_figure_num("chamber-s")`, `r s_figure_num("chamber-g")`).
Brief fluctuations to higher humidities were observed when chambers were opened to insert or remove samples (`r s_figure("chamber-s")`).

The GLMM including the effect of generation only was selected as the best-fitting model for DT (`r table("glmm")`). 
Sporophytes had `r sporo_dt_effect_mean` greater DT (95 % CI `r sporo_dt_effect_lower` to `r sporo_dt_effect_upper`) relative to gametophytes (`r table("glmm-pars")`).

@@

We found a wide variation of DT in filmy fern sporophytes on Moorea, from no tolerance in terrestrial species to tolerance of water potentials well below -200 MPa in some epiphytes.
Levels of similarly extreme DT have also been reported in other species of *Hymenophyllum* [@Proctor2003; @Proctor2012] and a general correlation of habitat with DT in filmy ferns has been previously established [@Shreve1911; @Proctor2003; @Proctor2012; @Parra2009; @Saldana2013], but no other studies to our knowledge have documented a similar range of DT values in filmy ferns from a single site.
One may wonder then, what is the adaptive significance of being able to withstand drying at -200 MPa vs. -100 MPa when the ambient water potential is typically > -5 MPa and only rarely, if ever, drops below -50 MPa.
The recent finding of a constitutive mechanism for DT in filmy ferns [@GarcesCea2014] supports the need for a relatively wide "safety margin," and similar (or even more extreme) levels of constitutive DT are well known in bryophytes [@Oliver1993].
The conservative behavior of fern stomata, which lack a response to the plant stress hormone ABA, is well documented [@Brodribb2011; @Mcadam2012; @Mcadam2013].
It is possible that filmy ferns also behave conservatively with respect to water-stress.
We suggest that the variation in DT observed here is relevant because it is correlated with habitat, and likely reflects overall physiological tolerance, not just artificial extremes.
For example, sporophytes of some high elevation epiphytes that we surveyed (*C. minutum* var. 2, *H. digitatum*, *H. multifidum*, *H. polyanthos*) seem to be able to better withstand intense vs. moderate desiccation, with higher recovery values at -282 and -86 MPa vs. -38 MPa when dry for 15 d.
This may be an adaptation to cloud forest conditions; although cloud forests are frequently moist due to constant fog, dry periods are intense during the times when there is no cloud cover.
The complete lack of DT in terrestrial species is not surprising, considering they have much more direct access to water than epiphytes and therefore substantially less selective pressure to maintain DT.
Since controls kept at 100% RH maintained F~v~/F~m~ values near pre-treatment levels in all sporophytes (`r s_figure("dt-control")`), it is unlikely that the lack of tolerance seen in terrestrial species is due solely to removal from the soil.
Comparison of DT with the minimum water potential envelope of each species (`r figure("corr")`) indicates that sporophytes of non-tolerant terrestrial and saxicolous species may not be able to occur in habitats with minimum water potential exceeding \circa{ }-7 MPa.
In contrast, habitats with minimum water potential below -7 MPa are nearly all epiphytic, and the filmy fern sporophytes occurring there are all capable of DT.

@@

Contrary to our hypotheses, gametophytes of filmy ferns are in general not more tolerant of the abiotic environment (light levels and water potential) than sporophytes.
This differs from other fern groups with desiccation tolerant gametophytes but desiccation sensitive sporophytes [@WatkinsJr.2007c].
In the filmy ferns we studied, DT levels of both sporophytes and gametophytes largely reflected habitat; in general, epiphytic species tended to have higher DT than terrestrial or saxicolous species, regardless of life stage.
Interestingly, this echoes much earlier field observations (not experimental data) by @Holloway1930 on filmy fern gametophytes in New Zealand: he reported apparent DT in gametophytes of *Hymenophyllum rarum* R. Br. and *H. villosum* Colenso, both high elevation epiphytes with desiccation tolerant sporophytes, and lack of DT in terrestrial filamentous gametophytes of *Polyphlebium colensoi* (Hook.) Ebihara & K. Iwats., *Abrodictyum strictum* (Menzies ex Hook. & Grev.) Ebihara & K. Iwats., and *A. elongatum* (A. Cunn.) Ebihara & K. Iwats. occupying moist, protected sites on the forest floor.
@WatkinsJr.2007c also found that DT of fern gametophytes tended to match habitat, with terrestrial species having lower DT than epiphytes.
However, we found that gametophytes had lower DT than sporophytes regardless of growth habit (`r figure("compare")`).
At high elevation sites (\ie, cloud forest), epiphytic ferns often occur in a dense matrix of bryophytes (Fig. 1B).
It is possible that this bryophyte cover helps to retain moisture during brief periods of drought and thus protect the epiphytic fern gametophytes that grow amongst them.
More detailed studies of the high elevation epiphytic environment and interactions between co-occurring gametophytes of ferns and bryophytes are needed to test this hypothesis.

Although we predicted that species with gametophytes that occur far beyond the range of their sporophytes would have higher DT, this was not the case.
This is perhaps best illustrated by *C. apiifolia* (`r figure("habit")`d, e, h).
Sporophytes of this species are usually restricted to moist cloud forest sites from \circa{ }600 m to 1200 m, but we observed gametophytes over a much wider range, down to 200 m.
A similar distribution pattern has been reported in congeneric *Callistopteris baldwinii* (D. C. Eaton) Copel.
from Hawaii [@Dassler1997].
Since gametophytes of *C. apiifolia* are common on Moorea and have a unique morphology [@Nitta2017], we were able to collect enough material of this species for additional tests of DT at higher humidity levels (48 h at 75% and 100% RH; results not shown).
However, it still failed to recover from even these gentle treatments.
This suggests that the widespread gametophytes of *C. apiifolia* do not rely on DT to attain their distribution, but instead must do so via some other mechanism.
Although we measured terrestrial microhabitats by positioning sensors a few cm above the ground, these sensors are still outside of the boundary layer.
It is likely that the gametophytes of *C. apiifolia* do not actually experience the conditions measured with our 'terrestrial' dataloggers, but instead grow within a much more consistently moist boundary layer.
Gametophytes of *C. apiifolia* produce gemmae (`r figure("habit")`e, h), and often form dense clonal mats.
In the case that their microhabitats do become too dry, they may suffer loss at the edge of the population, then recover by clonal growth [@Farrar2008].
Furthermore, the complex surface of clonal mats has been shown to increase the boundary layer and decrease evaporation rates in mosses [@Rice2001], and may function similarly in *C. apiifolia*.
Other filmy fern species also produce gemmae, but they are much more frequent in *C. apiifolia*, and the large size of the clonal mats formed by *C. apiifolia* indicate that it may have a high growth rate (J. Nitta, pers. obs.).
It is possible that there is a tradeoff between growth rate and DT, such that species capable of rapid asexual growth like *C. apiifolia* are unable to tolerate desiccation, but slower growing epiphytes such as *Hymenophyllum* spp.
can better tolerate it [@Oliver2000].
Growth rates of tolerant and non-tolerant gametophytes including quantification of gemmae production should be investigated in these species to test this hypothesis.

@@

Photosynthetic parameters did not vary significantly between species from different habitats.
Rather, we observed a clear intergenerational difference, with gametophytes consistently adapted for lower light levels than sporophytes (`r figure("combined")`, `r table("glmm")`).
In the only other study to our knowledge that compared photosynthetic rates between gametophytes and sporophytes of a filmy fern, @Johnson2000 also found that gametophytes of *V. speciosa* reached maximum ETR at lower levels than sporophytes: in gametophytes of this species, photosynthesis became saturated at a PPFD of 4--5 µmol·m^-2^·s^-1^ in the field or 30--50 µmol·m^-2^·s^-1^ in the lab vs. 30--50 µmol·m^-2^ ·s^-1^ for sporophytes (lab measurement only).
Although we found similar differences in direction between gametophytes and sporophytes, the measurements of @Johnson2000 are considerably lower than what we observed in the field for both Moorean filmy fern gametophytes (PPFD~95%~ \circa{ }40--60 µmol·m^-2^·s^-1^) and sporophytes (PPFD~95%~ \circa{ }130--160 µmol·m^-2^·s^-1^).
This makes sense in light of the fact that *V. speciosa* is an extremely deep-shade plant, with gametophytes occupying protected rock crevices that receive less than 1 µmol·m^-2^·s^-1^ PPFD for most of the day [@Johnson2000]; many of the gametophytes sampled in our study occur in more exposed conditions.
It is surprising, however, that we did not observe any differences between species in different habitats, given that light levels should vary between tree trunks and the forest floor, at least on a \circa{ }1 m scale.
It is possible that the actual light levels experienced by gametophytes growing in these habitats may not vary significantly if they occupy protected microsites such as bryophyte mats or crevices in rock or bark.

### 2021-02-03 ms/si.Rmd
Update MS

---
title: "SI"
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research-si.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

@@

**`r s_figure("chamber-s")`**. Conditions inside desiccation chamber and duration of desiccation treatment for sporophytes at most intense desiccation level. LiCl was used to maintain constant humidity at \circa{ }18%.

>>>>

---
title: ""
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research-si.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

**Electronic supplementary materials**

**Title:** Intergenerational niche differentiation in filmy ferns (Hymenophyllaceae)

**Authors:** Nitta JH; Watkins JE; Holbrook NM; Taputuarai R; Wang T; Davis CC

**Journal:** Journal of Plant Research

**Corresponding author:** Joel H. Nitta  
Department of Biological Sciences, Graduate School of Science, The University of Tokyo, 2-11-16 Yayoi, Bunkyo-ku, Tokyo, 113-0032, Japan  
Phone: +81-  
Fax: +81-  
email: joelnitta\@gmail.com

**Content:** \figs `r s_figure_num("tree")`--`r s_figure_num("light-curves")`

**`r s_figure("tree")`**. Maximum likelihood ultrametric phylogenetic tree including all Moorean filmy fern species.

**`r s_figure("chamber-s")`**. Conditions inside desiccation chamber and duration of desiccation treatment for sporophytes.

**`r s_figure("chamber-g")`**. Conditions inside desiccation chamber and duration of desiccation treatment for gametophytes.

**`r s_figure("range")`**. Elevational range (m) of sporophytes and gametophytes of filmy ferns on Moorea, French Polynesia.

**`r s_figure("dt-control")`**. Recovery of controls (samples kept on moist tissues) for desiccation tolerance test of filmy ferns from Moorea, French Polynesia.

**`r s_figure("water-all")`**. Relative water content (RWC) of sporophytes after desiccation by duration of desiccation treatment (2 or 15 days).

**`r s_figure("water-s")`**. Relative water content (RWC) of sporophytes during desiccation tolerance test.

**`r s_figure("light-curves")`**. Rapid light response curves of filmy ferns from Moorea, French Polynesia.

@@

**`r s_figure("chamber-s")`**. Conditions inside desiccation chamber and duration of desiccation treatment for sporophytes. LiCl was used to maintain constant humidity at \circa{ }18%.
